Ladies' figure skating in the 2002 Winter Olympics

### 2025-03-02 inst/skating.Rmd
tweaks

```{r,showskating}
set.seed(0)
skating_table <- ordertable(read.table("skating.txt", header=TRUE))
```

@@

```{r,convertordertosupport}
summary(suppfun(ordertable(skating_table)))
```

@@

```{r,threemedallists}
head(skating_table,2)
```

@@

```{r, tableofresults}
hughes    <- unlist(skating_table[1,])
slutskaya <- unlist(skating_table[2,])
table(hughes)
table(slutskaya)
```

>>>>

```{r,showskating}
set.seed(0)
skating_table <- ordertable(read.table("skating.txt", header=TRUE))
skating_table
```

@@

```{r,convertordertosupport}
summary(suppfun(skating_table))
```

@@

```{r,threemedallists}
skating_table[1:3]
```

@@

```{r, tableofresults}
hughes    <- unclass(skating_table)[1,]
slutskaya <- unclass(skating_table)[2,]
table(hughes)
table(slutskaya)
```
